Glyph-maps for visualizing climate data and models

### 2011-08-25 paper.tex
working on intro

\title{Glyph-maps for visualizing climate data and models}
\author{Cook, Hofmann, Wickham, Wickham, Cheng}

@@

@@

@@

Will first explore for regularly gridded data, a simple starting point and a common output of climate models, and then show a few simple extensions to deal with non-rectangular grids and irregular locations, as exemplified by raw climate data which is typically collect at irregular locations.

\begin{figure*}[htp]
\includegraphics[width=6in]{images/nasa-colored-map.png}
\caption{Facetted map of de-seasonalized temperature.}
\end{figure*}

\section{Generating a time series at each location}

\begin{figure*}[htp]
\centerline{\includegraphics[width=4in]{images/nasa-deseas-trend.pdf}}
\caption{Time series icon at each location, showing de-seasonalized trend.}
\end{figure*}

@@

\begin{figure}[htbp]
  \centering
  %\includegraphics[width=0.5\linewidth]{ref-line}%
  %\includegraphics[width=0.5\linewidth]{ref-box}
  \caption{caption}
  \label{fig:ref-basic}
\end{figure}

>>>>

\title{Glyph-maps for visualizing climate data and models}
\author{Cook, Hofmann, Wickham, Wickham}

@@

Climate data is usually composed of measurements on variables such as temperature, precipitation, and winds that have been collected from a spatial and temporal context. The classic display for spatial data is to use color or grey scale overlaid on geographic location, typically including a map. When measurements are made a different time periods also a common way to display the data is in small multiples, such as in Figure \ref{fig:facetted-map}. In this plot, a separate map is drawn for each month and year, over a 6 year period of remotely sensed temperature data above Central America. Color is used to display the de-seasonalized temperature measurements, with red being high values and blue being low values. The data  comes from \cite{NASA-Data-Expo}.

\begin{figure*}[htp]
\includegraphics[width=6in]{nasa-colored-map.png}
\caption{Facetted map of de-seasonalized temperature.}
\label{fig:facetted-map}
\end{figure*}

@@

\subsection{Glyph plots}

@@

Will first explore for regularly gridded data, a simple starting point and a common output of climate models, and then show a few simple extensions to deal with non-rectangular grids and irregular locations, as exemplified by raw climate data which is typically collect at irregular locations.
\section{Generating a time series at each location}

\begin{figure*}[htp]
\centerline{\includegraphics[width=4in]{nasa-deseas-trend.pdf}}
\caption{Time series icon at each location, showing de-seasonalized trend.}
\end{figure*}

@@

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.5\linewidth]{ref-line}%
  \includegraphics[width=0.5\linewidth]{ref-box}
  \caption{caption}
  \label{fig:ref-basic}
\end{figure}
